---
title: "Introduction to FlightDeck"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo = F, cache = F}
library(flightdeck)
library(htmltools)
knitr::opts_chunk$set(fig.cap = "", eval = FALSE)
```

<div class='well'>
The basic idea of `flightdeck` is to let users below powerful interactive dashboards by composing [widgets](../reference/index.html#section-widgets) into [panels](../reference/index.html#section-panels), [organizing](../reference/index.html#section-layouts) them on a page and assembling them into a [dashboard](../reference/index.html#section-dashboard).
</div>

You can create a simple dashboard in seven lines of code!


```{r}
library(flightdeck)
library(htmltools)
fdBoard(
  fdHeader(title = 'My Board'),
  fdSidebar(p("Hello World!")),
  fdBody()
)
```


To learn more about how to build dashboards using __flighdeck__, read the tutorial.

<a href='tutorial.html'>
<button class='btn btn-primary'>
 Goto Tutorial
 <i class='fa fa-chevron-right'></i>
</button>
</a>

<style>
.figure img {
  max-width: 100%;
  box-shadow: 1px 2px 20px 0px rgba(0,0,0,0.25);
  border: 1px solid #ccc;
  display: block;
  margin-left: auto;
  margin-right: auto;
  margin-bottom: 30px;
  margin-top: 30px;
}
.figure .caption {
  display: none;
}
</style>